openarchaeoCollaboration

### 2023-06-12 analysis/paper.qmd
Added this top matter so that I could run the code

@@

| Category                              | Kind      | Scope                                                                                                                                                                                                        |
|:-----------|:-----------|:------------------------------------------------|
| Packages and libraries                | Software  | Sets of functions assembled with clear purpose, and made accessible using standards established by an underlying platform.                                                                                   |
| Standalone software                   | Software  | Software that may be operated without needing to first access an underlying platform.                                                                                                                        |
| Scripts                               | Software  | Sets of pragmatically assembled mutable functions, often lacking complete documentation or adherence to protocols that would otherwise facilitate secondary use outside their original contexts of creation. |
| Specifications, protocols and schemas | Documents | A formal data structure or framework intended to be used as a model.                                                                                                                                         |
| Products                              | Documents | Stable outcomes of creative work.                                                                                                                                                                            |
| Guides                                | Documents | An educational resource or documented protocol meant to instruct readers how to apply relevant tools or techniques.                                                                                          |
| Lists and datasets                    | Documents | A series of consistently organized observations assembled with purpose.                                                                                                                                      |

@@

---

#### Notes from January 30, end of day
In cleaning the data we made a few significant decisions that revealed insights into our dataset. 
We constructed the user-user graph and filtered out several bots. 
We filtered out several large non-archaeology projects that effected the network in ways that distracted us from what we wanted to say about the archaeological community. 
We filtered isolates. 
We calculated the degree and betweenness to assess whether this was realistic representation of what we know. 
We wanted to figure out who are the key nodes, what they had in common. 
The people who are high betweenness are people who primarily produce computational archaeology code as a job. 
We can investgate further by comparing with some other measures of activity, like volume of commits or something else. 
We also looked at the same thing, but with only commits, or without commits. 
For the subgraph of non-commits, it includes many people from the commits-only or commits-included graphs, but also more people who do not commit as much.

>>>>

---
title: "openarchaeoCollaboration"
author:
  - name: Zack Batist
    url: https://zackbatist.info
    affiliation: Faculty of Information, University of Toronto
    orcid: 0000-0003-0435-508X 
  - name: Joe Roe
    url: https://joeroe.io
    affiliation: Institute of Archaeological Sciences, University of Bern
    orcid: 0000-0002-1011-1244
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r dependencies, include=FALSE}
library("fs")
library("geomtextpath")
library("ggiraph")
library("ggraph")
library("gt")
library("here")
library("khroma")
library("lubridate")
library("openarchaeoCollaboration")
library("patchwork")
library("tidygraph")
library("tidyverse")
library("here")
```

```{r plot-theme}
theme_oarch <- function() theme(
)
```

@@

| Category                              | Kind      | Scope                                                                                                                                                                                                        |
|:------------------|:------------------|:-----------------------------------|
| Packages and libraries                | Software  | Sets of functions assembled with clear purpose, and made accessible using standards established by an underlying platform.                                                                                   |
| Standalone software                   | Software  | Software that may be operated without needing to first access an underlying platform.                                                                                                                        |
| Scripts                               | Software  | Sets of pragmatically assembled mutable functions, often lacking complete documentation or adherence to protocols that would otherwise facilitate secondary use outside their original contexts of creation. |
| Specifications, protocols and schemas | Documents | A formal data structure or framework intended to be used as a model.                                                                                                                                         |
| Products                              | Documents | Stable outcomes of creative work.                                                                                                                                                                            |
| Guides                                | Documents | An educational resource or documented protocol meant to instruct readers how to apply relevant tools or techniques.                                                                                          |
| Lists and datasets                    | Documents | A series of consistently organized observations assembled with purpose.                                                                                                                                      |

@@

#### Notes from January 30, end of day

In cleaning the data we made a few significant decisions that revealed insights into our dataset. We constructed the user-user graph and filtered out several bots. We filtered out several large non-archaeology projects that effected the network in ways that distracted us from what we wanted to say about the archaeological community. We filtered isolates. We calculated the degree and betweenness to assess whether this was realistic representation of what we know. We wanted to figure out who are the key nodes, what they had in common. The people who are high betweenness are people who primarily produce computational archaeology code as a job. We can investgate further by comparing with some other measures of activity, like volume of commits or something else. We also looked at the same thing, but with only commits, or without commits. For the subgraph of non-commits, it includes many people from the commits-only or commits-included graphs, but also more people who do not commit as much.
